Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/methodology.tex
methodology: made smartphone questions italics too.

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios to control for the type of device being used. Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}:
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item How would you feel if an app on your <device> vibrated your phone without asking you first?
\item How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?
\item How would you feel if an app on your <device> un-muted a phone call without asking you first?
\item How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?
\item How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?
\end{enumerate}

>>>>

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios to control for the type of device being used. Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}:
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item {\it How would you feel if an app on your <device> vibrated your phone without asking you first?
\item How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?
\item How would you feel if an app on your <device> un-muted a phone call without asking you first?
\item How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?
\item How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?}
\end{enumerate}
